Playing with PCAs

### 2024-03-15 3-reports/playing_with_pcas.Rmd
cleaning

```{r}
## PCA input files ----
pca_overall = fit_pca_function(data_wide_PCA) 
pca_overall_wle = fit_pca_function(data_wide_PCA %>% filter(region == "WLE"))
pca_overall_cb = fit_pca_function(data_wide_PCA %>% filter(region == "CB"))
```

@@

```{r, fig.width=10, fig.height=6}
gg_pca_wle = 
  ggbiplot(pca_overall_wle$pca_int, obs.scale = 1, var.scale = 1,
           groups = as.character(pca_overall_wle$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=3,stroke=1, alpha = 1,
             aes(shape = pca_overall_wle$grp$site,
                 color = groups))+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wc"), 
                     values = pal_transect)+
  #scale_shape_manual(values = c(21, 19))+
  #scale_shape_manual(values = c(21, 21, 19), name = "", guide = "none")+
  xlim(-6,6)+
  ylim(-4.5,4.5)+
  labs(shape="",
       title = "PCA: WLE",
       subtitle = "surface horizons")+
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical")+
  NULL

>>>>

```{r}
## PCA input files ----
pca_overall = fit_pca_function(data_wide_PCA) 
pca_overall_wle = fit_pca_function(dat = data_wide_PCA %>% filter(region == "WLE"))
pca_overall_cb = fit_pca_function(data_wide_PCA %>% filter(region == "CB"))
```

@@

```{r, fig.width=10, fig.height=6}
gg_pca_wle = 
  ggbiplot(pca_overall_wle$pca_int, obs.scale = 1, var.scale = 1,
           groups = as.character(pca_overall_wle$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 1) +
  geom_point(size=3,stroke=1, alpha = 1,
             aes(shape = pca_overall_wle$grp$site,
                 color = groups))+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "wc"), 
                     values = pal_transect)+
  #scale_shape_manual(values = c(21, 19))+
  #scale_shape_manual(values = c(21, 21, 19), name = "", guide = "none")+
  xlim(-6,6)+
  ylim(-4.5,4.5)+
  labs(shape="",
       title = "PCA: WLE",
       subtitle = "surface horizons")+
  theme_kp()+
  theme(legend.position = "top", legend.box = "vertical")+
  NULL
